\chapter{Introduction}
\label{chp:introduction} 

\section{Motivation}
Today's largest online social network, Facebook, has increased drastically in popularity since it was introduced, and people share enormous amounts of information. During the lifetime of Facebook there has been a major change in the privacy and security settings. At the same time Facebook's features have been significantly upgraded (e.g., Apps), and the platform itself has expanded to several different platforms (e.g., iOS and Android). Owing to this development, the complexity of privacy-related issues has made the originally embedded privacy requirements inadequate. This makes it interesting to look into privacy issues related to Facebook, and find out how aware people are of the existence of the various settings. Facebook has for many also become a sort of "snopping"-tool and it is therefore important that the users are able to protect the information they do not want shared with the public.

Interdependency is a reciprocal relation between two or more decision-making entities, whose actions have consequences for each other. Interdependency is a very important issue when it comes to social networks, since your privacy is affected by the decisions of others. Applications on Facebook introduced a whole new dimension to the privacy issues and in particular issues regarding interdependent privacy. It is therefore interesting to look at people's awareness when it comes to the information they share with apps, and how apps utilize this information. Previous studies have shown that the apps' permission requests is often ambiguous, and that the permissions often goes against the users' privacy settings \cite{thirdPartyApps}.  


\section{Problem Description}
Based on our motivation we did research and conducted a survey in order to answer the following questions: 

\begin{enumerate}
\item What kind of settings does Facebook offer today?
\item How have the default privacy settings on Facebook evolved over time?
\item What are the default settings today?
\item What kind of features have Facebook introduced that at some point have affected the user's privacy?
\item How aware are the users of the settings on Facebook, and how often do they check them?
\item To what degree do people care about what they post about others (photos, comments etc.), and what others post about them? 
\item Is there a difference in what kind of settings people value depending on  demographics?
\item To what degree are people aware of the different permissions Facebook apps request, and do they know the meaning of interdependent privacy?
\end{enumerate}



\section{Methodology}
\label{sec:methodology}
Our assignment is divided into parts, where one consists of collecting data from Facebook users regarding their view on Facebook privacy settings, and the other is a theoretical research of how Facebook privacy settings has evolved since the introduction of Facebook. This means that we have used different approaches to be able to retrieve the information desired.

\paragraph{}
In this section we will describe our approach of collecting data from Facebook users regarding their view on Facebook privacy settings. Facebook is a global social network, so to be able to get more accurate information it is important to reach out to a wide and diverse audience. We decided to use Amazon Mechanical Turk for this purpose. To gather the data, we made a survey for the users to answer. Survey is a common used research method that involves the use of standardized questionnaires or interviews to collect data about people and their preferences, thoughts and behaviours in a systematic manner \cite{survey}. Survey, as a research method, has several advantages in comparison to other methods of doing research. Survey is a good method of retrieving unobservable data, like for example peoples attitudes, behaviours, characteristics, preferences, and demographics. Surveys are great when you want to cover a large group of people, like a country, that otherwise would be difficult to observe. With large groups and large amounts of data, surveys allows small effects to be detected, and makes it easy to compare the subgroups that may appear. Survey are in an economically sense cost effective. It is a lot cheaper for a researcher to make and send out a survey than to use other methods like experimental research. Survey as a research method also has some disadvantages. The method is often exposed to biases, like sampling bias, non-response bias, and social desirability bias. Surveys have a reputation for low responses, hence the non-response bias. This was one of the reasons for choosing AMT as a platform for publishing your survey. 

We started by implementing the survey in Amazon Mechanical Turk (AMT), but learned that the templates provided by AMT was missing some of the features we wished to include, like dividing the questions into several pages. So mainly for design purposes we chose to create our survey in SurveyMonkey. This is easily integrated with AMT and a often used option.  Using SurveyMonkey also made it a lot easier to keep track of answers and see summaries. SurveyMonkey has a great and easily understandable user interface, and made it easy to share the survey to other mediums like Facebook, to reach out to an even larger and more diverse audience. 

\paragraph{}
In AMT we set the requirements that the users had to be "Master Workers". This is users that through a good reputation has earned the title, and by setting this requirement we rule out unserious users and answers. This will save us a lot of time in the screening process. When a user chooses to take our survey, they first get some information about the purpose and incentive of the survey, and a link to SurveyMonkey to take the survey. When the survey is finished the user receives a code that they have to provide before submitting their HIT in AMT. This is an assurance for us that all users on AMT has finished the survey before they get paid. Throughout the lifetime of our survey we have changed this code, just to make sure that nobody tries to get paid without actually doing the work. When the survey is completed in a serious manner the workers get paid \$1,5. On average, the users spent 13 minutes and 24 seconds to take the survey, this gives an effective hourly rate of \$6,7. 

\section{Limitations} 
Our main limitation is the amount of time available to finalize our specialization project. We only had 4 months at our disposal. Our research analysis is based on the 250 responses we got on our survey. This is not enough to get a full and accurate image on the research area, but give a solid basis for further work. The amount of money granted for conducting the research was also limited, this mean we could not pay an unlimited amount of workers on AMT. In addition to this, it is not an infinite number of workers available on AMT. If we were to reach out to even more people, we would need to use several different arenas. Our results are only based on the analysis from the survey. We did not implement anything or create a "tool" in order to cover a wider field in our research. Even though we distributed our survey on AMT and Facebook, it is up to the user whether or not to take the survey. We had no control over the users' intentions. A normal problem with surveys is that there exists no way for us as researchers to verify that the respondents have answered in a truthful and proper manner. Another factor to have in mind, is the overlooking of valuable research data when conducting an analysis. 


